---
title: "Project1"
author: "Arushi Arora"
date: "9/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# importing the libraries
library(stringr)
```

#### Reading the file
```{r warning=FALSE}
# replaced local file with url, becuase had issues on RPub, on reading file

# https://statisticsglobe.com/r-readlines-example
# path <- getwd()
# my_txt <- readLines(paste(path, "/tournamentinfo.txt", sep = ""))

file_url <- "https://raw.githubusercontent.com/Araisedtotwo/Project01/master/tournamentinfo.txt"
input_data <- readLines(file_url)
# Printing the table headers along with first row
print(head(input_data))
```
#### Remving the header rows
```{r}
# https://stackoverflow.com/questions/37770938/how-to-remove-first-n-rows-in-a-data-set-in-r
N <- 4
processed_data <- tail(input_data, -N)
print(head(processed_data))

# length of processed data
len <- length(processed_data)
print(c("length of processed data is :",len))
```

### Extracting the required fields

##### Required fields : Player’s Name, Player’s State, Total Number of Points, Player’s Pre-Rating, and Average Pre Chess Rating of Opponents

```{r}
players_name <- c()
total_points <- c()
players_state <- c()
player_pre_rating <- c()
opponent_pre_rating <- c()
```
#### Filling data in our variables from the data

###### Extracting the fields available directly in data
 - player name
 - total points scored
 - player state
 - player pre-rating
```{r}
# https://stackoverflow.com/questions/1699046/for-each-row-in-an-r-dataframe

get_pre_rating <- function(processed_data, player_idx) {
    row <- processed_data[(3 * player_idx) - 1]
    row_vector <- unlist(str_split(row,"\\|"))
    temp <- str_extract(row_vector[2],"R: [ [0-9]]+")  
    pre_rating_val <- str_extract(temp,"[[0-9]]+")
    return (pre_rating_val)
}

for (i in 1: len){
  
  if ((i - 1) %% 3 == 0){
    row <- processed_data[i]
    row2 <- processed_data[i+1]
    
    # https://stringr.tidyverse.org/reference/str_split.html
    row_list <- str_split(row,"\\|")  # list type
    row_list2 <- str_split(row2,"\\|")  # list type

    row_vector <- unlist(row_list)
    row_vector2 <- unlist(row_list2)
    
    # Obtaining the player name, trimming whitespaces
    player_name <- str_trim(row_vector[2])
    
    # Obtaining the player name, trimming whitespaces
    player_name <- str_trim(row_vector[2])

    # Adding player_name to corresponding vector
    # https://www.geeksforgeeks.org/adding-elements-in-a-vector-in-r-programming-append-method/
    players_name <- append(players_name, player_name)

    # Obtaining the player state, trimming whitespaces
    player_state <- str_trim(row_vector2[1])
    
    # Adding player_state to corresponding vector
    players_state <- append(players_state, player_state)

    # Obtaining Total Number of Points for player and converting to int
    player_points <- str_trim(row_vector[3])

    # Adding player_points to corresponding vector
    total_points <- append(total_points, player_points)

    # Obtaining the player number, trimming whitespaces
    player_num <- str_trim(row_vector[1])

    # Obtaining the player's pre-rating , trimming whitespaces
    pre_rating <- get_pre_rating(processed_data,as.numeric(player_num))

    # Adding pre_rating to corresponding vector
    player_pre_rating <- append(player_pre_rating, pre_rating)

    # Obtaining the average pre_rating of opponents for taking their average
    oponnent_pre_rating_values <- c() 

    for (j in 4:10){
      opponent_status = row_vector[j]
      
      # Check if data valid,contains W, L or D
      # https://stackoverflow.com/questions/10128617/test-if-characters-are-in-a-string
      if(grepl("W", opponent_status) || grepl("L", opponent_status) || grepl("D", opponent_status)){
        
        oponnent_id <- str_extract(str_trim(row_vector[j]),"[\\d]+")
        oponnent_pre_rating <- get_pre_rating(processed_data,as.numeric(oponnent_id))
        oponnent_pre_rating_values <- append(oponnent_pre_rating_values, as.numeric(oponnent_pre_rating))
        
      }
    }
    average_opp_pre_rating <- as.integer(round(mean(oponnent_pre_rating_values), digits = 0))
    
    # Adding player_num to corresponding vector
    opponent_pre_rating <- append(opponent_pre_rating, average_opp_pre_rating)
  }
}
```

#### Final Data Merging and Printing

```{r}

output <- data.frame(players_name, 
                    players_state, 
                    total_points = as.numeric(total_points), 
                    player_pre_rating = as.numeric(player_pre_rating),
                    "average_opponents_pre_rating"=opponent_pre_rating)
print(output)
```

#### Storing R dataframe as CSV
```{r}
# https://stackoverflow.com/questions/40595317/how-do-i-write-a-csv-from-r-without-quoted-values
write.table(output, file="tournament_summery.csv", sep=",", row.names = FALSE, quote=FALSE)
# write.csv(output,"tournament_summery.csv", row.names = FALSE)
```